### 2018-08-13 introduction.tex
grammar and whatnot

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced type of reactor which was developed at \gls{ORNL} 
in the 1950s and was operated in the 1960s. More recently, \gls{MSR} was 
included in the six advanced reactor concepts that have been chosen by the 
Generation IV International Forum (GIF) for further research and development. 
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid coolant which is also a fuel.

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
 materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
 elements}F$_3$) are mixed with carrier salts to form a liquid fuel which is 
 circulated in a loop-type primary circuit \cite{haubenreich_experience_1970}. 
 This innovation leads to immediate advantages over traditional, solid-fueled, 
 reactors. These include near-atmospheric pressure in the primary loop, 
 relatively high coolant temperature, outstanding neutron economy, a high level 
 of inherent safety, reduced fuel preprocessing, and the ability to 
 continuously remove fission products and add fissile and/or fertile elements 
 \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
 early 1970s by \gls{ORNL} specifically to realize the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
 continuous fuel reprocessing, \gls{MSBR} is very attractive to effecively 
 realize advantages of the thorium fuel cycle because the $^{233}$U bred from 
 $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
 $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
 ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
 ($\tau_{1/2}$=26.967d).} being recycled back to the core 
 \cite{betzler_modeling_2016}. The mixture of LiF-BeF$_2$-ThF$_4$-UF$_4$ has a 
 melting point of $499^\circ$C, a low vapor pressure at operating temperatures, 
 and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
 In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
 quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
 cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
 for transmutation of spent fuel from current \glspl{LWR}.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
\glspl{MSR} amon the six advanced reactor concepts promising for further 
research and development.
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

 In the thermal spectrum \gls{MSR}, fluorides of fissile and/or fertile 
 materials (i.e. UF$_4$, ThF$_4$,  PuF$_3$, TRU\footnote{ Transuranic 
 elements}F$_3$) combine with carrier salts to form a liquid fuel that 
 circulates in a loop-type primary circuit \cite{haubenreich_experience_1970}.  
 Immediate advantages over traditional, solid-fueled, reactors include 
 near-atmospheric pressure in the primary loop, 
 relatively high coolant temperature, outstanding neutron economy, improved 
 safety parameters, reduced fuel preprocessing, and the ability to 
 continuously remove fission products and add fissile and/or fertile elements 
 \cite{leblanc_molten_2010}. The thorium-fueled \gls{MSBR} was developed in the 
 early 1970s by \gls{ORNL} to explore the promise of the thorium 
 fuel cycle, which uses natural thorium instead of enriched uranium. With 
 continuous fuel reprocessing, the \gls{MSBR}
 realizes the advantages of the thorium fuel cycle because the $^{233}$U bred from 
 $^{232}$Th is almost instantly \footnote{\space $^{232}$Th transmutes into 
 $^{233}$Th after capturing a neutron. Next, this isotope decays to $^{233}$Pa 
 ($\tau_{1/2}$=21.83m), which finally decays to $^{233}$U 
 ($\tau_{1/2}$=26.967d).} recycled back to the core 
 \cite{betzler_modeling_2016}. The chosen fuel salt, 
 LiF-BeF$_2$-ThF$_4$-UF$_4$, has a $499^\circ$C melting point, a low vapor 
 pressure at operating temperatures, 
 and good flow and heat transfer properties \cite{robertson_conceptual_1971}. 
 In the matter of nuclear fuel cycle, the thorium cycle produces a reduced 
 quantity of plutonium and \glspl{MA} compared to the traditional uranium fuel 
 cycle. Finally, the \gls{MSR} also could be employed as a converter reactor 
 for transmutation of spent fuel from current \glspl{LWR}.
